func-descr.template

### 2025-10-31 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Functions described: CreateRMSEs_ResultTibble, RMSEs.AddRow.

Let's begin our analysis by evaluating the simplest model described in [Section 23.3 *A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_23-3], and then gradually refine it through further research.

>>>>

Let's begin our analysis by evaluating the simplest model described in [Section 25.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_25-1], and then gradually refine it through further research.

### 2025-10-31 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: CreateRMSEs_ResultTibble, RMSEs.AddRow.

::: {.noteblock data-latex=""}
The source code of the [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
:::
:::

#### [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) Function {#func.mse_cv}
\

@@

The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) function is shown below:
```{r eval=FALSE}
mse_cv <- function(r_list) {
  mses <- sapply(r_list, mse(r))
  mean(mses)
}
```

::: {.noteblock data-latex=""}
The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
:::
:::

@@

::: {.noteblock data-latex=""}
The source code of the [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L10) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) script on _GitHub_.
:::
:::

@@

::: { #func.rmse2.args.predicted_ratings .sidebar }
  - **predicted_ratings:** A numeric vector representing a set of *predicted rating values* computed from the data stored in the test dataset.

@@

::: {.noteblock data-latex=""}
The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L12) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) script on _GitHub_.
:::
:::

@@

#### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.}
\

::: {.noteblock data-latex=""}
The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) script on _GitHub_.
:::

::: { #func.RMSEs.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
```
:::

::: { #func.RMSEs..args .sidebar }
##### Arguments
\

::: { #func.RMSEs..args.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;

@@

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.details .sidebar }
##### Details
\

::: { #func.RMSEs.code .sidebar }
##### Source Code
\

The soure code of the function is provided below:
```{r eval=FALSE}
```
:::

The modified _Resut (RMSEs) Table_.

#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) Function {#func.RMSEs.AddRow}
\

::: {.noteblock data-latex=""}
The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) script on _GitHub_.
:::

@@

::: { #func.RMSEs.AddRow.args.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;

@@

@@

The soure code of the function is provided below:
```{r eval=FALSE}
RMSEs.AddRow <- function(RMSEs, 
                         method, 
                         value, 
                         comment = "", 
                         before = NULL){
  RMSEs |>
    add_row(Method = method,
            RMSE = value,
            Comment = comment,
            .before = before)
}
```
:::

The modified _Resut (RMSEs) Table_.

@@

::: { #func.RMSEs.AddDiffColumn.args.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;

@@

The modified _Resut (RMSEs) Table_.

@@

Prints the _Resut (RMSEs) Table_.

@@

::: { #func.RMSE_kable.args.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;

@@

::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;

>>>>

::: {.noteblock data-latex=""}
The source code of the [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
:::
:::

#### [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) Function {#func.mse_cv}
\

@@

The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is shown below:
```{r eval=FALSE}
mse_cv <- function(r_list) {
  mses <- sapply(r_list, mse(r))
  mean(mses)
}
```

::: {.noteblock data-latex=""}
The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
:::
:::

@@

::: {.noteblock data-latex=""}
The source code of the [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) script on _GitHub_.
:::
:::

@@

::: { #func.rmse2.args.predicted_ratings .sidebar }
  - **predicted_ratings:** A numeric vector representing a set of *predicted rating* values computed from the data stored in the test dataset.

@@

::: {.noteblock data-latex=""}
The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) script on _GitHub_.
:::
:::

@@

#### [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) Function {#func.CreateRMSEs_ResultTibble}
\

Creates a _Result (RMSEs) Table_ of type *data frame*.
::: { #func.CreateRMSEs_ResultTibble.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
RMSEs.ResultTibble <- CreateRMSEs_ResultTibble()
```
:::

::: { #func.CreateRMSEs_ResultTibble.args .sidebar }
##### Details
\

This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame representing the _Result (RMSEs) Table_ to store the _RMSE_ values for every model used in the project to predict movie ratings.

The result data frame, which is returned to the client code, has the following columns:

  - *Method* (chr);
  - *RMSE* (num);
  - *Comment* (chr)

::: { #func.CreateRMSEs_ResultTibble.value .sidebar }
##### Value
\

A tibble returned by the internally called [tibble::tibble()](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble)

@@

::: { #func.CreateRMSEs_ResultTibble.code .sidebar }
##### Source Code
\

The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) function is shown below:
```{r eval=FALSE}
CreateRMSEs_ResultTibble <- function(){
  tibble(Method = c("Project Objective"),
         RMSE = project_objective,
         Comment = " ")
}
```
:::

::: {.noteblock data-latex=""}
The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) script on _GitHub_.
:::

#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) Function {#func.RMSEs.AddRow}
\

Adds a row to the original _Result (RMSEs) Table_ passed in the [RMSEs](#func.RMSEs.AddRow.args.RMSEs) argument.

@@

::: { #func.RMSEs.AddRow.args.RMSEs .sidebar }
  - ***RMSEs:*** Original _Resut (RMSEs) Table_ (of type *data frame*) to modify;

@@

::: { #func.RMSEs.AddRow.code .sidebar }
##### Details
\

This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame representing the original _Result (RMSEs) Table_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.

::: { #func.RMSEs.AddRow.value .sidebar }
##### Value
\

The modified tibble returned by the internally called [tibble::add_row()](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row).

@@

The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) function is shown below:
```{r eval=FALSE}
RMSEs.AddRow <- function(RMSEs, 
                         method, 
                         value, 
                         comment = "", 
                         before = NULL){
  RMSEs |>
    add_row(Method = method,
            RMSE = value,
            Comment = comment,
            .before = before)
}
```
:::

::: {.noteblock data-latex=""}
The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) script on _GitHub_.
:::

@@

::: { #func.RMSEs.AddDiffColumn.args.RMSEs .sidebar }
  - ***RMSEs:*** _Result (RMSEs) Table_ to modify;

@@

The modified _Result (RMSEs) Table_.

@@

Prints the _Result (RMSEs) Table_.

@@

::: { #func.RMSE_kable.args.RMSEs .sidebar }
  - ***RMSEs:*** _Result (RMSEs) Table_ to print;

@@

::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
  - ***RMSEs:*** _Result (RMSEs) Table_ to print;

### 2025-10-31 reports/capstone-movielens.site/work/func-descr.template.Rmd
Functions described: CreateRMSEs_ResultTibble, RMSEs.AddRow.

>>>>

#### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.RMSEs.}
\

Modifies the original _Result (RMSEs) Table_ passed in the [RMSEs](#func.RMSEs..args.RMSEs) argument.

::: { #func.RMSEs..usage .sidebar }
##### Usage
\

```{r eval=FALSE}
```
:::

::: { #func.RMSEs..args .sidebar }
##### Arguments
\

::: { #func.RMSEs..args.RMSEs .sidebar }
  - ***RMSEs:*** Original _Resut (RMSEs) Table_ (of type *data frame*) to modify;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs..args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.details .sidebar }
##### Details
\

This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame representing the original _Result (RMSEs) Table_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
:::
::: { #func.RMSEs..value .sidebar }
##### Value
\

The modified tibble returned by the internally called [tibble::()]().

::: { #func.RMSEs..code .sidebar }
##### Source Code
\

The source code of the [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```
:::

::: {.noteblock data-latex=""}
The source code of the [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
:::
